TorresEspin-2021

### 2025-01-08 doc/charting/Niso-2022.qmd
created table of overall study characteristics and corrected some information in the charting forms

---
title: 'Charting for Niso et al 2022'
---

Review for  Niso-2022: Open and reproducible neuroimaging: From study inception to publication

# Title of publication

@@

-   Type of paper (e.g., tips, example): guide (to conduct open science), review (of existing tools).
-   Themes (e.g., tools, organization): organization.
-   Other keywords (e.g., newcomers): all science cycle

@@

Utilizing private devices for data acquisition, which leads to black boxes and difficults comparision.    
Struggle with derivative data sharing. Which format should be the best for data that we generate from the available raw standardized data? Here they propose BrainLife as an example, but in other fields this is a very interesting topic!

>>>>

---
title: 'Niso-2022'
---

# Open and reproducible neuroimaging: From study inception to publication

@@

-   Type of paper (e.g., tips, example): guide (to conduct open
    science), review (of existing tools).
-   Themes (e.g., tools, organization): tools, workflow
-   Other keywords (e.g., newcomers): all science cycle

@@

Utilizing private devices for data acquisition, which leads to black
boxes and difficults comparision.\
Struggle with derivative data sharing. Which format should be the best
for data that we generate from the available raw standardized data? Here
they propose BrainLife as an example, but in other fields this is a very
interesting topic!

### 2025-01-08 doc/charting/TorresEspin-2021.qmd
created table of overall study characteristics and corrected some information in the charting forms

-   Type of paper (e.g., tips, example):
    -   Case study
    -   Example workflow
-   Themes (e.g., tools, organization):
    -   tools
    -   organization
-   Other keywords (e.g., newcomers):
    -   Data infrastructure
    -   FAIR data
    -   Case study
    -   Agile design
    -   Templates
    -   Examples
    -   Strategies
    -   Software development

@@

::: content-hidden
For instance: "OSF; pre-registration; planning". You can mention
multiple tools. Just make another bullet.

The research process is: planning, conducting, analysing, disseminating.
If a combination write several, if all write "all"
:::

@@

::: content-hidden
For instance: "designing the project - preregistration - creating the
experiment - recruitment and data collection - data analysis -
dissemination".

These are overall process highlights
:::

>>>>

-   Type of paper (e.g., tips, example):
    -   example
    -   workflow
-   Themes (e.g., tools, organization):
    -   tools
    -   organization
-   Other keywords (e.g., newcomers):
    -   Data infrastructure
    -   FAIR data
    -   Case study
    -   Agile design
    -   Templates
    -   Examples
    -   Strategies
    -   Software development

@@

@@
